\documentclass[11pt, a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=blue
}

% AI : section formatting - bold rule underline style
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{7pt}{3pt}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.1em}

\setlength{\parskip}{3pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Henry Routson} \\[4pt]
  \href{mailto:Henry_Rou@ProtonMail.com}{Henry\_Rou@ProtonMail.com}
  \quad|\quad 0419 108 859
  \quad|\quad \href{https://www.linkedin.com/in/henryroutson/}{linkedin.com/in/henryroutson}
\end{center}

\noindent
Extensive knowledge and experience in modern AI systems and Software Engineering.
Currently working as an AI Engineer.

\vspace{2pt}

% ── Two-column body ──────────────────────────────────────────────────────────
\setlength{\columnsep}{14pt}
\begin{multicols}{2}

% ── Education ────────────────────────────────────────────────────────────────
\section{Education}

\textbf{The University of Melbourne} \\
Bachelor of Science, Computing and Software Systems --- \textit{Distinction}

\textbf{The University of Melbourne} \\
Master of Computer Science, AI --- \textit{in progress, part time}
\begin{itemize}
  \item NLP: Fine Tuning, Prompt Tuning, Transformers, Hugging Face
\end{itemize}

\textbf{Ballarat Grammar}
\begin{itemize}
  \item Academic scholarship
  \item VCE: Software Development, Specialist \& Methods Mathematics, Chemistry, Physics
\end{itemize}

% ── Open-Source ───────────────────────────────────────────────────────────────
\section{Open-Source Contributions}

\textbf{Cached File Explorer} (Rust) \\
\href{https://github.com/conaticus/FileExplorer/pull/47}{github $\cdot$ FileExplorer/pull/47}
\begin{itemize}
  \item Ultra-fast file explorer using caching and low-level Rust.
  \item Fixed a poisoned thread issue from multi-threading
\end{itemize}

\textbf{Supabase SQL Auth UI} \\
\href{https://github.com/supabase-community/flutter-auth-ui/pull/108}{github $\cdot$ flutter-auth-ui/pull/108}
\begin{itemize}
  \item Added options and documentation to the auth UI.
\end{itemize}

\textbf{LlamaIndex} \\
\href{https://github.com/run-llama/llama_index/pull/17393}{github $\cdot$ llama\_index/pull/17393}
\begin{itemize}
  \item Fixed bugs, added features, improved code quality in the Notion reader.
\end{itemize}

% ── Achievements ─────────────────────────────────────────────────────────────
\section{Achievements}

\textbf{Antler VC Build Hackathon}, 1st Place \hfill Jun 2026 \\
\href{https://www.antler.co/}{antler.co} \quad|\quad \href{https://luma.com/build-the-hackathon?tk=3hiTHC}{Event page}
\begin{itemize}
  \item Won 1st place and \$7,500 prize at Antler's two-day build sprint in Sydney.
  \item Built \href{https://auto-pipeline.dev/}{auto-pipeline.dev} and \href{https://auto-pipeline-app.dev/}{auto-pipeline-app.dev} in 14 hours.
\end{itemize}

% ── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\textbf{KPMG}, AI Engineer \hfill Jun 2025 -- Present \\
\href{https://kpmg.com/au/en.html}{kpmg.com/au/en.html}
\begin{itemize}
  \item AI Prototype Engineer in Futures, working with LLMs and agent frameworks.
  \item Developed standardised codebase (34k lines) to automate prompting, parsing, validation, and deep research.
  \item Automated assessment of 10k pages of legislation equivalent.
  \item Created pipeline for SQL migration and database merging.
  \item Deployed Transformer models to CUDA GPUs with Hugging Face and Ollama.
  \item Built autonomous agent system with RLMs; multi-agent and sub-agent implementation.
  \item \textit{Skills:} Azure, FastAPI, LangChain, LangExtract, Pandas, Docker.
\end{itemize}

\textbf{Bet Right}, Data Science Intern \hfill Jan 2025 -- Apr 2025 \\
\href{https://www.linkedin.com/company/bet-right/}{linkedin/bet-right}
\begin{itemize}
  \item SQL, Snowflake, Databricks, PowerBI, Azure, DevOps.
  \item Improved abuse detection ML model by 15--40\% using stacking.
\end{itemize}

\textbf{DSCubed}, DS/AI Team Vice Head \hfill Nov 2024 -- Jul 2025 \\
\href{https://www.dscubed.org.au/}{dscubed.org.au}
\begin{itemize}
  \item RAG, vector databases, LLM frameworks and APIs.
  \item Contributed to LlamaIndex open-source project.
\end{itemize}

\textbf{ARES}, University of Melbourne \hfill 2023 \\
\href{https://www.linkedin.com/company/aresunimelb}{linkedin/aresunimelb}
\begin{itemize}
  \item 3D front-end software for rocket trajectory simulation across supersonic and subsonic speeds.
\end{itemize}

\textbf{LeetCode:} \href{https://leetcode.com/u/HenryRoutson/}{leetcode.com/u/HenryRoutson}

% ── Projects ──────────────────────────────────────────────────────────────────
\section{Projects}

\textbf{IT Project} (JS/TS, React) \hfill \href{https://dev-aia.vercel.app/}{dev-aia.vercel.app}
\begin{itemize}
  \item Quicksort visualisation; redesigned stack visualisation and improved code quality.
\end{itemize}

\textbf{LLM Experiments} \hfill \href{https://github.com/HenryRoutson/llm_experiments}{github/llm\_experiments}
\begin{itemize}
  \item Transformers, JAX, Keras, PyTorch; combining pre-training and supervised fine-tuning.
\end{itemize}

\textbf{Auto Avail} (JS/TS) \hfill \href{https://github.com/HenryRoutson/Auto_Avail}{github/Auto\_Avail}
\begin{itemize}
  \item when2meet-style scheduler using location data to generate continuous availability periods.
  \item Stack: Supabase, Flutter, React Native, Postgres, pgTAP, Expo, TypeScript.
\end{itemize}

\textbf{CHelp} (C) \hfill \href{https://github.com/HenryRoutson/CHelp}{github/CHelp}
\begin{itemize}
  \item Valgrind alternative: tracks dynamic allocations and catches memory issues early.
\end{itemize}

\textbf{Autoheader} (Rust) \hfill \href{https://github.com/HenryRoutson/autoheader}{github/autoheader}
\begin{itemize}
  \item Automatically generates C header files.
\end{itemize}

% ── References ────────────────────────────────────────────────────────────────
\section{References}

Available upon request.
\begin{itemize}
  \item \textbf{Cindy} --- AI Engineer, KPMG. \href{https://www.linkedin.com/in/runxin-liu/}{LinkedIn}
  \item \textbf{Pranav} --- L3 Data Scientist, NAB. \href{https://www.linkedin.com/in/pranavjayanty/}{LinkedIn}
\end{itemize}

\end{multicols}

\end{document}
